Integrating brain and biomechanical models - a new paradigm for understanding neuro-muscular control

### 2017-12-08 papers/integration/omm_integ.tex
Changes based on proof reading the last section of the discussion and the figure captions.

\rvw{\cite{pearson_whiskerbot:_2007} describes a wheeled robot which has a
biomimetic whisker sensory system, along with a biomimetic neural
system imitating the operation of the rat's sensory processing and
controlling the movement of the robot. \cite{fend_artificial_2004} is
a similar, wheeled, whiskered robot, with a repertoire of three
behaviours organised in a subsumption architecture. In both robots,
actions that are selected within the brain model drive a
non-biologically accurate wheel motor control algorithm to achieve
rotational and translational movements. Although both have sensory and
processing systems which are guided by biology, the non-biological
motor control stage prevents us from considering these as being
studies of computational neurobehaviour. Instead, we would refer to
these as \e{embodied models}, as described
in \cite{bolado-gomez_biologically_2013}, a study in which the
learning behaviour of a biomimetic `core' model is embedded within an
engineered `architecture' (a wheeled robot) which closes the
agent-environment loop.}
%
\rvw{\cite{yu_development_2004} report on a biomimetic fish robot,
whose motor system closely resembles that of the real fish. The robot
is able to operate in a closed-loop mode, where sensory input is
provided to the non-biomimetic control algorithms from overhead
cameras, but its control system is also able to operate in open-loop
mode. Neither the control system, nor the sensory system are
biologically accurate and we would not describe this study as
computational neurobehaviour. Nevertheless, the biomechanically accurate
motor system they describe has the potential to form part of a
computational neurobehavioural study of swimming behaviour in the
fish, if it were combined in a loop with suitable sensory input and
sensory processing models.}
%
\rvw{\cite{knips_neural_2017} is a report of a reach-and-grasp robot
arm controlled via a dynamic neural field brain model. The sensory
input for this system---its `eyes'---is a Microsoft Kinect sensor; it
also has somatosensory feedback from the fingers of the robot's
hand. The neural field `brain' controls the seven degrees of freedom
of the arm to carry out the reach-and-grasp action. While this robot
has closed-loop control and is clearly inspired by biology, it remains
a study of robotics and of the improvement of the control of the
robot's reach-and-grasp function, rather than a study which aims to
learn more about the biology of a primate arm. For this reason, we
would describe the study of \cite{knips_neural_2017} as an embodied
model.}

\rvw{To summarise, in most closed-loop robotic studies which
incorporate neuromimetic models, the hardware forms an `engineered
surround architecture', allowing for the examination of the behaviour
of the embodied model. However, suitably \e{biomimetic} hardware such as
the fish in \cite{yu_development_2004} would not be excluded from
computational neurobehavioural studies.}

@@

\rvw{Thus, while there are many models that close the
agent-environment loop and display partial biological plausibility,
the biomimetic features are usually confined to a sub-system of the
entire model. This leads us to formalise a definition of computational
neurobehaviour as: \e{The study of biological sensory-motor system
behaviour using biologically accurate models of sensory input, brain
and motor sub-systems operating in a closed-loop}.}
%
% Another computational neurobehavioural study?
\rvw{We believe our oculomotor model is one of the first such models
using this approach and shares many features with that
of \cite{arena_motor-skill_2017} which describes a robotic insect
system based on the fly species \e{Drosophila Melanogaster}. It has
biomimetic insect legs implemented in a virtual robot and a
neuromimetic brain. Closing the loop is a visual sensory input system
which is able to determine the distance between the robot and an
obstacle and the obstacle's height. The authors demonstrate that the
virtual robot is able to learn to climb obstacles in a realistic
manner and suggest that the model may be compared with experimental
data from future Drosophila experiments addressing obstacle climbing
and learning. The visual system is not described in detail, but if it
is modelled in a biologically plausible manner, then this work may
reasonably be described as a computational neurobehaviour study,
contemporaneous with our own.}

@@

% Figure 1
\begin{figure}[h!]
\begin{center}
\includegraphics[width=\textwidth]{./figures/ccg_model.png}
\end{center}
\caption{ \bol{a) The macroscopic architecture of the \ccg~model.} The main
nuclei modelled as brain systems are: basal ganglia (BG), frontal eye
fields (FEF), thalamus (THAL) and superior colliculus (SC). The
retinal input is presented via non-biologically plausible retinal
populations. The loops through basal ganglia, which define the
architecture, are shown with coloured lines: the cortical loop
(through FEF and THAL) in green and the sub-cortical loop (through SC
and THAL) in blue. Connections with arrowheads indicate excitatory
connections, those with circles are inhibitory. A red border indicates
that the box represents a sub-system of two or more populations; a
black box indicates (at least, within the context of the model) a
single neural population. The BG box is expanded in: \bol{b) The basal
ganglia model component.}
%
This shows a basal ganglia comprising striatum (Str\_D1 \& Str\_D2),
subthalamic nucleus (STN), globus pallidum externum (GPe) and
substantia nigra reticulata (SNr). The model has three action channels
shown as black boxes within each blue population border. Three
channels of cortical input to the BG are also depicted. Red indicates
the activation level of a given channel, helping to illustrate the
selection mechanism. For example, the channel indicated by the
leftmost bar has a high salience (cortical input) and excites activity
in Str\_D1 which then inhibits the leftmost bar in SNr. The diffuse
projection from STN is equivalent to summing its projections
channel-wise, and then projecting the sum to all channels of its
target populations (the blue arrows indicate that all channels of GPe
and SNr are targeted by the connection). Dopaminergic modulation of
the inputs to the striatum are indicated by the blue circles labelled
`d' and the dotted lines. The SNr sends inhibitory output projections
to its targets. \bol{c) 2D Gaussian weights.} The `GaussianKernel'
connectivity pattern is based on the `in-plane displacement' between
the location of a neural element in one layer, and the location of a
target neural element in the target layer for the connection. The
potential weight of the connection is given by a 2D Gaussian function,
which is maximum for the target neuron which exactly corresponds to
the source neuron, and drops down for target neurons which are
horizontally displaced from the source neuron. A threshold is applied
to avoid a computationally expensive all-to-all connectivity (with
most of these connections having negligible weight values).  If the
weight is non-zero, then a connection is made from source to target,
otherwise no connection is made. \bol{d) Gaussian connectivity.} This
image shows connectivity (green rays) from two source neurons (in
Str\_D2, brown spheres) to target neurons (in GPe, blue spheres). The
circular connectivity pattern is seen. This does not show the weight
\e{values}, which reduce `towards the edge of the circle' and follow the
relationship shown in (c).}
\label{fig:ccg_model}
\end{figure}

% Figure 2
\begin{figure}[h!]
\begin{center}
\includegraphics[width=0.9\textwidth]{./figures/Brain_Model.png}
\end{center}
\caption{ The brain model. This is the SpineCreator `network layer' view of
the model. Each box represents a neural population with 2500 elements,
arranged in a 50$\times$50 grid. The SpineML component name is printed
on the bottom right corner of each population box and the population
name is at the top. The overall connectivity between populations is
represented by the projection arrows with the colour indicating the
connectivity scheme (one-to-one connections are red, Gaussian kernel
connections are dark blue and so on). Excitatory connections have
arrowheads and inhibitory connections have circles, although for
details of the behaviour of the connections, the weight-update and
post-synapse components must be studied. Briefly, the model comprises
a \e{World} population, into which a retinotopically organised view of
the world is introduced. This information is passed into cortical
populations (FEF) and subcortical populations (SC) via a simple model
of the retina. These feed a cortico-thalamo-basal ganglia loop, which
selects which region of the deep layer of superior colliculus should
be disinhibited, allowing activity to build up therein. The five
populations comprising the basal ganglia are enclosed in a grey
outline. Note that substantia nigra pars compacta is not modelled
here, instead the level of dopamine in the striatum is set via a
parameter in the Str\_D1 and Str\_D2 populations}
\label{fig:brainmodel}
\end{figure}

% Figure 3
\begin{figure}[h!]
\begin{center}
\includegraphics[width=0.9\textwidth]{./figures/mapping.png}
\end{center}
\caption{ Representative mapping from eye's frame of reference in Cartesian
co-ordinates to retinotopic co-ordinates. (a) The mapping of
luminances in the eye's frame of reference. The world input is
pre-defined by a JSON configuration file. Luminance position, size and
shape can be defined in this file, along with the times at which
luminances appear and disappear. The worldDataMaker.cpp code computes
the locations of the luminances in the eye's frame of reference, given
its rotational state. It also computes a 2D Gaussian convolution of
the luminances. Here, there are two cross shaped luminances spanning
10\dg, one of value 0.8 at the fixation point (0,0) and one of value
0.5 at a peripheral position (0,-12\dg). Note that these crosses have
the same `bar width' of 2\dg~as the crosses used in the simulations,
but their span of 10\dg~is greater than the 6\dg~used in the
simulations, to make these images clearer. (b) The locations of the
luminances in the eye's frame of reference are then converted into
retinotopic co-ordinates, with centrally located luminances being
represented at low values of $r$ and more peripheral luminances having
higher values of $r$. $\phi$ encodes rotational angle: 1 and 50 encode
upward movement; 13 is left; 25 is down; 37 is right. The output of
the World component is fed into FEF\_add\_noise and into the retinal
neuron populations. The colour map makes it possible to distinguish
between the two crosses. (c) The FEF\_add\_noise populations adds a
level of noise to the signal representing processing of the signal in
visual cortex. (d) A Gaussian projection from FEF\_add\_noise to FEF
further blurs the activity in FEF. FEF is the input to the basal
ganglia and one input to superior colliculus.}
\label{fig:mapping}
\end{figure}

% Figure 4
\begin{figure}[h!]
\begin{center}
\includegraphics[width=0.6\textwidth]{./figures/Brain_Stem_1channel.png}
\end{center}
\caption{ One pair of channels of the saccadic burst generator (SBG) for left
(cyan) or right (green) movements. Collicular activity in SC\_avg
excites the channels via SBG weight maps. Each box represents a neural
population and shows the population name, the number of neural
elements (here 2500 or 1) and the SpineML component name; \e{LIN} for
Leaky integrator or \e{integrator}. Key: LLBN: Long lead burst
neurons; IBN: Inhibitory burst neurons; OPN: Omnipause neurons; EBN:
Excitatory burst neurons; TN: Tonic neurons; MN: Motoneurons.}
\label{fig:sbg}
\end{figure}

% Figure 5
\begin{figure}[h!]
\begin{center}
\includegraphics[width=0.5\textwidth]{./figures/eye_screen_plus.png}
\end{center}
\caption{ The biomechanical eye. a) an OpenSim rendering of a pair of
biomechanical eyes showing the positions of the extraocular
muscles. Note that i) volume visualization of muscles should not be
confused with FEM muscle models; it is provided for user feedback
purposes, i.e. shape and color change depending on the muscle
activation, ii) superior and inferior oblique are visualized up to
their respective muscle pulleys. b) OpenSim rendering of biomechanical
eye within a head model c) Top-down schematic cross-sectional view of
the biomechanical eye situated within a spherical screen, with a
horizontal rotation towards a luminances at an angle of $-\theta_{y}$
about the $y$ axis. The $y$ axis points up, out of the page.}
\label{fig:bioeye}
\end{figure}

\begin{figure}[h!]
\begin{center}
\includegraphics[width=0.9\textwidth]{./figures/model_framework.png}
\end{center}
\caption{ The model framework. The model is specified using a combination of
declarative XML files and hand-coded C++. These original model
specifications are shown within the blue box. b) The green box shows
the processes which are applied to the model specification to produce
the BRAHMS system. Most of the process is defined within the scripts
which make up \stob, but the hand-written components must be manually
compiled and installed within the BRAHMS Namespace, allowing the
BRAHMS executable to locate them at runtime. c) The red box shows the
resulting BRAHMS system ready to be executed by the BRAHMS
executable. In practice, this call is made by \stob.}
\label{fig:modelframework}
\end{figure}

\begin{figure}[h!]
\begin{center}
\includegraphics[width=0.9\textwidth]{./figures/scdeep_plus.png}
\end{center}
\caption{ a) \& b) Tabareau-style weight maps for `left' and `down' components
of a saccade. c) The two weight maps in a) and b) shown on the same
graph, viewed from above. Circles show the locations of potential
hills of activity. Purple, dashed circles encode saccades down;
red circles encode saccades with both a left and a down component. d)
Showing the additional deep layer of superior colliculus (SC\_deep2)
and the output layer (SC\_avg, named for the fact that in an earlier
version of the model, it received the output of the centroid of
SC\_deep).  The widening Gaussian projection is shown as the arrow
between SC\_deep and SC\_deep2.}
\label{fig:scdeep}
\end{figure}

\begin{figure}[h!]
\begin{center}
\includegraphics[width=0.8\textwidth]{./figures/sacc_vs_targetpos.png}
\end{center}
\caption{ Accuracy at different target eccentricities for fixation luminance
0.2 and target luminance 0.3.}
\label{fig:saccvstarg}
\end{figure}

\begin{figure}[h!]
\begin{center}
\includegraphics[width=\textwidth]{./figures/weightmaps.png}
\end{center}
\caption{ Weight maps for the connections between the output layer of superior
colliculus and the six long lead burst neurons of the saccadic burst
generator model. Each map increases exponentially with increasing $r$,
multiplied by cosine($\phi$) about its `active' axis.}
\label{fig:weightmaps}
\end{figure}

\begin{figure}[h!]
\begin{center}
\includegraphics[width=0.95\textwidth]{./figures/errorsurface_TModel3.png}
\end{center}
\caption{ The end-point error surface for the original, na\"ive model
(TModel3). a) The ratio of the magnitudes of the total error vector
and the target vector, expressed as a percentage. b) The ratio of the
magnitude of the $x$ component of the error vector to the magnitude of
the target vector, expressed as a percentage. c) As (b) but for the
$y$ component. d) As (b), for $z$ component. All colour maps are shown
with the same scale. The target rotations, $\theta_{x}^t$ and
$\theta_{y}^t$ are denoted `Target X' and `Target Y' in the figure.}
\label{fig:errorsurfaceTM3}
\end{figure}

\begin{figure}[h!]
\begin{center}
\includegraphics[width=0.95\textwidth]{./figures/errorsurface.png}
\end{center}
\caption{ The end-point error surface for the model in which a widening
projection field was added to the model of the superior colliculus. a)
The ratio of the magnitudes of the total error vector and the target
vector, expressed as a percentage. b) The ratio of the magnitude of
the $x$ component of the error vector to the magnitude of the target
vector, expressed as a percentage. c) As (b) but for the $y$
component. d) As (b), for $z$ component. All colour maps are shown
with the same scale. The target rotations, $\theta_{x}^t$ and
$\theta_{y}^t$ are denoted `Target X' and `Target Y' in the figure.
Note that the range of the colour scale is 0 to 20\%, a much smaller
range than the range in Fig~\ref{fig:errorsurfaceTM3}.}
\label{fig:errorsurface}
\end{figure}

\begin{figure}[h!]
\begin{center}
\includegraphics[width=0.8\textwidth]{./figures/outmany.png}
\end{center}
\caption{ Representative single saccades. a) Trajectories from 9 saccades to a
single target at 9 different locations. In each case, a fixation cross
luminance of magnitude 0.2 was displayed at (0,0), the start position
of the eye, until time 0.4~s. The target luminance, magnitude 0.3 was
illuminated at time 0.4~s. Trajectory shape is dependent on the target
position, and there is a variable amount of error in the end-points
achieved by the model. Colour is used in this diagram as an aid to
distinguishing different saccades and their targets; for a given
saccade, the target location is given by the cross of the same colour
closest to the end of the trajectory. b) The three rotational
components of the `blue' saccade, to target location (-7,-7). c) The
three rotational components of the `red' saccade, to target location
(0,-10).}
\label{fig:outmany}
\end{figure}

\begin{figure}[h!]
\begin{center}
\includegraphics[width=0.8\textwidth]{./figures/lat_vs_everything.png}
\end{center}
\caption{ Exploring saccade latencies. a) Latency to first movement as a
function of target eccentricity for horizontal targets. b) Latency
vs. eccentricity for vertical targets. c) Latency vs. gap at three
different luminance values. The data are shown alongside
the \ccg~model results from Fig.~5 of \cite{cope_basal_2017} in blue,
and the experimental results used in that model in red. The fixation
luminance for the \ccg~curve was 0.5, the target lumianance 0.6 and
the target eccentricity was 8\dg. The difference between
the \ccg~model data and the data from the current model results from
the different mechanism by which activity in SC\_deep causes a
movement, the differing target angle and the reduced fixation
luminance used here. d) The effect
of the dopamine parameter on saccade latencies in gap, step and
overlap conditions, for two different target luminances.  e) Saccade
vs. luminance showing gradual transition between reflexive and express
behaviour.
%f) Saccade duration vs. saccade eccentricity for horizontal
%(rightwards), vertical (downwards) and 45\dg~oblique (down \& right) saccades.
}
\label{fig:latvsall}
\end{figure}

\begin{figure}[h!]
\begin{center}
\includegraphics[width=0.8\textwidth]{./figures/outrtn.png}
\end{center}
\caption{ There and back - a saccade to a target, followed by return to the
original fixation. a) Out and return saccade to a target at (0,-10\dg)
b) Rotational components of the saccade shown in (a). c) Outward and
return trajectories for the saccade shown in (a) alongside saccades to
three other targets.}
\label{fig:outrtn}
\end{figure}

>>>>

\rvw{\cite{pearson_whiskerbot:_2007} describe a wheeled robot which has a
biomimetic whisker sensory system, along with a biomimetic neural
system imitating the operation of the rat's sensory processing and
controlling the movement of the robot. \cite{fend_artificial_2004} is
a similar, wheeled, whiskered robot, with a repertoire of three
behaviours organised in a subsumption architecture. In both robots,
actions that are selected within the brain model drive a
non-biologically accurate motor control algorithm to achieve
rotational and translational movements. Although both have sensory and
processing systems which are guided by biology, the non-biological
motor control stage prevents us from considering these as being
studies of computational neurobehaviour. Instead, we would refer to
these as \e{embodied models}, as described
in \cite{bolado-gomez_biologically_2013}, a study in which the
learning behaviour of a biomimetic `core' model is embedded within an
engineered `architecture' (a wheeled robot) which closes the
agent-environment loop.}
%
\rvw{\cite{yu_development_2004} report on a biomimetic fish robot,
whose motor system closely resembles that of the real fish. The robot
is able to operate in a closed-loop mode, where sensory input is
provided to the non-biomimetic control algorithms from overhead
cameras, but its control system is also able to operate in open-loop
mode. Neither the control system, nor the sensory system are
biologically accurate and we would not describe this study as
computational neurobehaviour. Nevertheless, the biomechanically accurate
motor system they describe has the potential to form part of a
computational neurobehavioural study of swimming behaviour in the
fish, if it were combined in a loop with suitable sensory input and
sensory processing models.}
%
\rvw{\cite{knips_neural_2017} is a report of a reach-and-grasp robot
arm controlled via a dynamic neural field brain model. The sensory
input for this system---its `eyes'---is a Microsoft Kinect sensor; it
also has somatosensory feedback from the fingers of the robot's
hand. The neural field `brain' controls the seven degrees of freedom
of the arm to carry out the reach-and-grasp action. While this robot
has closed-loop control and is clearly inspired by biology, it remains
a study of robotics and of the improvement of the control of the
robot's reach-and-grasp function, rather than a study which aims to
learn more about the biology of a primate arm. For this reason, we
would describe the study of \cite{knips_neural_2017} as an embodied
model.}

\rvw{To summarise, in most closed-loop robotic studies which
incorporate neuromimetic models, the hardware forms an `engineered
surround architecture' allowing for the examination of the behaviour
of the embodied model. However, suitably \e{biomimetic} hardware such as
the fish in \cite{yu_development_2004} would not be excluded from
computational neurobehavioural studies, especially if movement is by
biomimetic muscle actuators \citep{wilson_cerebellar-inspired_2016,ohalloran_review_2008}.}

@@

\rvw{Thus, while there are many models that close the
agent-environment loop and display partial biological plausibility,
the biomimetic features are usually confined to a sub-system of the
entire model. This leads us to formalise a definition of computational
neurobehaviour as: \e{The study of biological sensory-motor system
behaviour using biologically accurate models of sensory input, brain
and motor sub-systems operating in a closed-loop}.}
%
% Another computational neurobehavioural study?
\rvw{We believe our oculomotor model is one of the first such models
using this approach and shares many features with that
of \cite{arena_motor-skill_2017} which describes a robotic insect
system based on the fly species \e{Drosophila Melanogaster}. It has
biomimetic insect legs implemented in a virtual robot and a
neuromimetic brain. Closing the loop is a visual sensory input system
which is able to determine the distance to an
on-coming obstacle and the obstacle's height. The authors demonstrate that the
virtual robot is able to learn to climb in a realistic
manner and suggest it may be compared with experimental
data from future Drosophila experiments addressing obstacle climbing
and learning. The visual system is not described in detail, but if it
is modelled in a biologically plausible manner, then this work may
reasonably be described as a computational neurobehaviour study,
contemporaneous with our own.}

@@

% Figure 1
\begin{figure}[!ht]
\begin{center}
\includegraphics[width=\textwidth]{./figures/ccg_model.png}
\end{center}
\caption{ \bol{a) The macroscopic architecture of the \ccg~model.} The main
nuclei modelled as brain systems are: basal ganglia (BG), frontal eye
fields (FEF), thalamus (THAL) and superior colliculus (SC). The
retinal input is presented via non-biologically accurate retinal
populations. The loops through basal ganglia, which define the
architecture, are shown with coloured lines: the cortical loop
(through FEF and THAL) in green and the sub-cortical loop (through SC
and THAL) in blue. Connections with arrowheads indicate excitatory
connections, those with circles are inhibitory. A red border indicates
that the box represents a sub-system of two or more populations; a
black box indicates (at least, within the context of the model) a
single neural population. The BG box is expanded in: \bol{b) The basal
ganglia model component.}
%
This shows a basal ganglia comprising striatum (Str\_D1 \& Str\_D2),
subthalamic nucleus (STN), globus pallidum externum (GPe) and
substantia nigra reticulata (SNr). The model has three action channels
shown as black boxes within each blue population border. Three
channels of cortical input to the BG are also depicted. Red indicates
the activation level of a given channel, helping to illustrate the
selection mechanism. For example, the channel indicated by the
leftmost bar has a high salience (cortical input) and excites activity
in Str\_D1 which then inhibits the leftmost bar in SNr. The diffuse
projection from STN is equivalent to summing its projections
channel-wise, and then projecting the sum to all channels of its
target populations (the blue arrows indicate that all channels of GPe
and SNr are targeted by the connection). Dopaminergic modulation of
the inputs to the striatum are indicated by the blue circles labelled
`d' and the dotted lines. The SNr sends inhibitory output projections
to its targets. \bol{c) 2D Gaussian weights.} The `GaussianKernel'
connectivity pattern is based on the in-plane component of the
displacement between
the location of a neural element in one layer, and the location of a
target neural element in the target layer for the connection. The
potential weight of the connection is given by a 2D Gaussian function,
which is maximum for the target neuron which exactly corresponds to
the source neuron, and drops down for target neurons which are
horizontally displaced from the source neuron. A threshold is applied
to avoid a computationally expensive all-to-all connectivity (with
most of these connections having negligible weight values).  If the
weight is non-zero, then a connection is made from source to target,
otherwise no connection is made. \bol{d) Gaussian connectivity.} This
image shows connectivity (green rays) from two source neurons (in
Str\_D2, brown spheres) to target neurons (in GPe, blue spheres). The
circular connectivity pattern is seen. This does not show the weight
\e{values}, which reduce `towards the edge of the circle' and follow the
relationship shown in (c).}
\label{fig:ccg_model}
\end{figure}

% Figure 2
\begin{figure}[!ht]
\begin{center}
\includegraphics[width=0.9\textwidth]{./figures/Brain_Model.png}
\end{center}
\caption{ The brain model. This is the SpineCreator `network layer' view of
the model. Each box represents a neural population with 2500 elements,
arranged in a 50$\times$50 grid. The SpineML component name is printed
on the bottom right corner of each population box and the population
name is at the top. The overall connectivity between populations is
represented by the projection arrows with the colour indicating the
connectivity scheme (one-to-one connections are red, Gaussian kernel
connections are dark blue and so on). Excitatory connections have
arrowheads and inhibitory connections have circles, although for
full details of the behaviour of the connections, the weight-update and
post-synapse component associated with each connection must be
referred to. Briefly, the model comprises
a \e{World} population, into which a retinotopically organised view of
the world is introduced. This information is passed into cortical
populations (FEF) and subcortical populations (SC) via a simple model
of the retina. These feed a cortico-thalamo-basal ganglia loop, which
selects which region of the deep layer of superior colliculus should
be disinhibited, allowing activity to build up therein. The five
populations comprising the basal ganglia are enclosed in a grey
outline. Note that substantia nigra pars compacta is not modelled
here, instead the level of dopamine in the striatum is set via a
parameter in the Str\_D1 and Str\_D2
populations. \bol{a)} Fixation cross input in Cartesian eye
frame. \bol{b)} Fixation cross input in retinotopic
co-ordinates. \bol{c)} Fixation cross with noise added. \bol{d)}
After blurring, input is passed to BG populations.}
\label{fig:brainmodel}
\end{figure}

% Figure 3
\begin{figure}[!ht]
\begin{center}
\includegraphics[width=0.9\textwidth]{./figures/mapping.png}
\end{center}
\caption{ Representative mapping from eye's frame of reference in Cartesian
co-ordinates to retinotopic co-ordinates. \bol{a)} The mapping of
luminances in the eye's frame of reference. The world input is
pre-defined by a JSON configuration file. Luminance position, size and
shape can be defined in this file, along with the times at which
luminances appear and disappear. The worldDataMaker.cpp code computes
the locations of the luminances in the eye's frame of reference, given
its rotational state. It also computes a 2D Gaussian convolution of
the luminances. Here, there are two cross shaped luminances spanning
10\dg, one of value 0.8 at the fixation point (0,0) and one of value
0.5 at a peripheral position (0,-12\dg). Note that these crosses have
the same `bar width' of 2\dg~as the crosses used in the simulations,
but their span of 10\dg~is greater than the 6\dg~used in the
simulations, to make these images clearer. \bol{b)} The locations of the
luminances in the eye's frame of reference are then converted into
retinotopic co-ordinates, with centrally located luminances being
represented at low values of $r$ and more peripheral luminances having
higher values of $r$. $\phi$ encodes rotational angle: 1 and 50 encode
upward movement; 13.5 is left; 26 is down; 38.5 is right. The output of
the World component is fed into FEF\_add\_noise and into the retinal
neuron populations. The colour map makes it possible to distinguish
between the two crosses. \bol{c)} The FEF\_add\_noise populations adds a
level of noise to the signal representing processing of the signal in
visual cortex. \bol{d)} A Gaussian projection from FEF\_add\_noise to FEF
further blurs the activity in FEF. FEF is the input to the basal
ganglia and one input to superior colliculus.}
\label{fig:mapping}
\end{figure}

% Figure 4
\begin{figure}[!ht]
\begin{center}
\includegraphics[width=0.6\textwidth]{./figures/Brain_Stem_1channel.png}
\end{center}
\caption{ One pair of channels of the saccadic burst generator (SBG) for left
(cyan) or right (green) movements. Collicular activity in SC\_avg
excites the channels via SBG weight maps, which are encoded as
explicit lists of connection weights in the blue connection arrows
from SC\_avg to the LLBN populations. Each box represents a neural
population and shows the population name, the number of neural
elements (here 2500 or 1) and the SpineML component name; \e{LIN} for
Leaky integrator or \e{integrator}. Key: LLBN: Long lead burst
neurons; IBN: Inhibitory burst neurons; OPN: Omnipause neurons; EBN:
Excitatory burst neurons; TN: Tonic neurons; MN: Motoneurons.}
\label{fig:sbg}
\end{figure}

% Figure 5
\begin{figure}[!ht]
\begin{center}
\includegraphics[width=0.5\textwidth]{./figures/eye_screen_plus.png}
\end{center}
\caption{ The biomechanical eye. \bol{a)} an OpenSim rendering of a pair of
biomechanical eyes showing the positions of the extraocular
muscles. Note that i) volume visualization of muscles should not be
confused with FEM muscle models; it is provided for user feedback
purposes, i.e. shape and color change depending on the muscle
activation, ii) superior and inferior oblique are visualized up to
their respective muscle pulleys. \bol{b)} OpenSim rendering of biomechanical
eye within a head model \bol{c)} Top-down schematic cross-sectional view of
the biomechanical eye situated within a spherical screen, with a
horizontal rotation towards a luminance at an angle of $-\theta_{y}$
about the $y$ axis. The $y$ axis points up, out of the page.}
\label{fig:bioeye}
\end{figure}

\begin{figure}[!ht]
\begin{center}
\includegraphics[width=0.9\textwidth]{./figures/model_framework.png}
\end{center}
\caption{ The model framework. The model is specified using a combination of
declarative XML files and hand-coded C++. These original model
specifications are shown within the blue box. \bol{b)} The green box shows
the processes which are applied to the model specification to produce
the BRAHMS system. Most of the process is defined within the scripts
which make up \stob, but the hand-written components must be manually
compiled and installed within the BRAHMS Namespace, allowing the
BRAHMS executable to locate them at runtime. \bol{c)} The red box shows the
resulting BRAHMS system ready to be executed by the BRAHMS
executable. In practice, this call is made by \stob.}
\label{fig:modelframework}
\end{figure}

\begin{figure}[!ht]
\begin{center}
\includegraphics[width=0.9\textwidth]{./figures/scdeep_plus.png}
\end{center}
\caption{ \bol{a)} \& \bol{b)} Tabareau-style weight maps for `left' and `down' components
of a saccade. \bol{c)} The two weight maps in (a) and (b) shown on the same
graph, viewed from above. Circles show the locations of potential
hills of activity. Purple, dashed circles encode saccades down;
red circles encode saccades with both a left and a down component. \bol{d)}
Showing the additional deep layer of superior colliculus (SC\_deep2)
and the output layer (SC\_avg, named for the fact that in an earlier
version of the model, it received the output of the centroid of
SC\_deep).  The widening Gaussian projection is shown as the arrow
between SC\_deep and SC\_deep2.}
\label{fig:scdeep}
\end{figure}

\begin{figure}[!ht]
\begin{center}
\includegraphics[width=0.8\textwidth]{./figures/sacc_vs_targetpos.png}
\end{center}
\caption{ Accuracy of single saccades at different target eccentricities for fixation luminance
0.2 and target luminance 0.3.}
\label{fig:saccvstarg}
\end{figure}

\begin{figure}[!ht]
\begin{center}
\includegraphics[width=\textwidth]{./figures/weightmaps.png}
\end{center}
\caption{ Weight maps for the connections between the output layer of superior
colliculus and the six long lead burst neurons of the saccadic burst
generator model. Each map increases exponentially with increasing $r$,
multiplied by cosine($\phi$) about its `active' axis.}
\label{fig:weightmaps}
\end{figure}

\begin{figure}[!ht]
\begin{center}
\includegraphics[width=0.95\textwidth]{./figures/errorsurface_TModel3.png}
\end{center}
\caption{ The end-point error surface for the original, na\"ive model
(TModel3). \bol{a)} The ratio of the magnitudes of the total error vector
and the target vector, expressed as a percentage. \bol{b)} The ratio of the
magnitude of the $x$ component of the error vector to the magnitude of
the target vector, expressed as a percentage. \bol{c)} As (b) but for the
$y$ component. \bol{d)} As (b), for $z$ component. All colour maps are shown
with the same scale. The target rotations, $\theta_{x}^t$ and
$\theta_{y}^t$ are denoted `Target X' and `Target Y' in the figure.}
\label{fig:errorsurfaceTM3}
\end{figure}

\begin{figure}[!ht]
\begin{center}
\includegraphics[width=0.95\textwidth]{./figures/errorsurface.png}
\end{center}
\caption{ The end-point error surface for the model in which a widening
projection field was added to the model of the superior colliculus. \bol{a)}
The ratio of the magnitudes of the total error vector and the target
vector, expressed as a percentage. \bol{b)} The ratio of the magnitude of
the $x$ component of the error vector to the magnitude of the target
vector, expressed as a percentage. \bol{c)} As (b) but for the $y$
component. \bol{d)} As (b), for $z$ component. All colour maps are shown
with the same scale. The target rotations, $\theta_{x}^t$ and
$\theta_{y}^t$ are denoted `Target X' and `Target Y' in the figure.
Note that the range of the colour scale is 0 to 20\%, a much smaller
range than the range in Fig~\ref{fig:errorsurfaceTM3}.}
\label{fig:errorsurface}
\end{figure}

\begin{figure}[!ht]
\begin{center}
\includegraphics[width=0.8\textwidth]{./figures/outmany.png}
\end{center}
\caption{ Representative single saccades. \bol{a)} Trajectories from 9 saccades to a
single target at 9 different locations. In each case, a fixation cross
luminance of magnitude 0.2 was displayed at (0,0), the start position
of the eye, until time 0.4~s. The target luminance, magnitude 0.3, was
illuminated at time 0.4~s. Trajectory shape is dependent on the target
position, and there is a variable amount of error in the end-points
achieved by the model. Colour is used in this diagram as an aid to
distinguishing different saccades and their targets; for a given
saccade, the target location is given by the cross of the same colour
closest to the end of the trajectory. \bol{b)} The three rotational
components of the `dark blue' saccade, to target location (-7,-7). \bol{c)} The
three rotational components of the `red' saccade, to target location
(0,-10).}
\label{fig:outmany}
\end{figure}

\begin{figure}[!ht]
\begin{center}
\includegraphics[width=0.8\textwidth]{./figures/lat_vs_everything.png}
\end{center}
\caption{ Exploring saccade latencies. \bol{a)} Latency to first movement as a
function of target eccentricity for horizontal targets. \bol{b)} Latency
vs. eccentricity for vertical targets. \bol{c)} Latency vs. gap at three
different luminance values. The data are shown alongside
the \ccg~model results from Fig.~5 of \cite{cope_basal_2017} in blue,
and the experimental results used in that model in red. The fixation
luminance for the \ccg~curve was 0.5, the target luminance 0.6 and
the target eccentricity was 8\dg. The difference between
the \ccg~model data and the data from the current model results from
the different mechanism by which activity in SC\_deep causes a
movement, the differing target angle and the reduced fixation
luminance used here. \bol{d)} The effect
of the dopamine parameter on saccade latencies in gap, step and
overlap conditions, for two different target luminances.  \bol{e)} Saccade
vs. luminance showing gradual transition between reflexive and express
behaviour.
%f) Saccade duration vs. saccade eccentricity for horizontal
%(rightwards), vertical (downwards) and 45\dg~oblique (down \& right) saccades.
}
\label{fig:latvsall}
\end{figure}

\begin{figure}[!ht]
\begin{center}
\includegraphics[width=0.8\textwidth]{./figures/outrtn.png}
\end{center}
\caption{ There and back - a saccade to a target, followed by return to the
original fixation. \bol{a)} Out and return saccade to a target at
(0,-10\dg). The outward trajectory is shown in blue, the return in pink.
\bol{b)} Rotational components of the saccade shown in (a). \bol{c)} Outward and
return trajectories for the saccade shown in (a) alongside saccades to
three other targets.}
\label{fig:outrtn}
\end{figure}

\begin{figure}[!ht]
\begin{center}
\includegraphics[width=0.8\textwidth]{./figures/doublesteps.png}
\end{center}
\caption{ Double steps. The effect of illuminating a first target at 8\dg~or
12\dg, followed by a second target at 12\dg~or 8\dg. \bol{a)} Horizontal
rotation of the eye plotted vs.~time for a saccade to the 12\dg~target
only (red), and to an 8\dg~target at 0.4~s followed by a 12\dg~target
after 30~ms (blue) or 40~ms (black). The timings are indicated by
vertical lines. When the second target is presented up to 30~ms after
the initial target, the initial target has not had time to dominate
the output saccade and a saccade to a location close to the second
target is made. If the delay is 40~ms or more, the activity from the
initial target has time to cause a built up of actiivty in SC\_deep
and an initial saccade close to the first target is made, followed,
after a longer than usual latency period, with a second saccade closer
to the second target. In this graph, the mean of five separate
simulations is plotted along with $\pm$1 standard deviation around the
mean. \bol{b)} The $\theta_{x}$/$\theta_{y}$ trajectories corresponding to
the data presented in (a).}
\label{fig:doublesteps}
\end{figure}
